### 2021-02-19 architecture.tex
Reference the GCN description from Evaluation
Add a todo

\subsection{\Gls{gcn}: From graphs to symbol embeddings}

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for the correctly ranking the symbol in the observed symbol precedences.
The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},
\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier. MS: sounds good.}
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules---one module per edge type.
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then repeatedly updates the embeddings by passing them through convolutional layers.
\todo{Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}

>>>>

\subsection{\Gls{gcn}: From graphs to symbol embeddings}
\label{sec:gcn}

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for correctly ranking the symbol in the observed symbol precedences.
The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},
\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier. MS: sounds good.}
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules---one module per edge type.
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then repeatedly updates the embeddings by passing them through convolutional layers.
\todo{Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}
